---
title: "Figure 2 plots"
author: "Martin Loza"
---

This is the main workflow to reproduce the Jurkat/293t cells correction plots in Figure 2.

```{r setup}
library(here)
library(patchwork)
library(Seurat)
library(ggplot2)
library(ggrepel)
options(future.globals.maxSize = 4e10)
source(here("Functions.R"))

resultsFile <- here("Data/Figure2")
plotsFile <- here("Figure2")
mytheme <- theme_classic() + theme(text = element_text(size = 20), legend.text=element_text(size=16))
theme_set(mytheme)
```

# Load data

```{r}
datal <- readRDS(file = paste0(resultsFile, "/datal.Rds"))
scores <- readRDS(file = paste0(resultsFile, "/scores.RDS"))
scoresKbet <- scores$scoresKbet
scoresSilhouette <- scores$scoresSilhouette
```

## Setup assay

We want to plot CD3D and XIST gene expressions, but they were not selected as variable features during integrations. Then, we add the original assay to the corrections.

```{r}
RNA <- Seurat::Assays(datal[["Seurat"]], slot = "RNA")
methods <- names(datal)
datal <- lapply(methods, function(m){
  object <- datal[[m
                   ]]
  if(m == "Uncorrected")
    object[["RNA2"]] <- RNA
  else
    object[["RNA"]] <- RNA
  
  return(object)
})
names(datal) <- methods

# Set max value for color pallete
maxExp = max(GetAssayData(datal[["Uncorrected"]], assay = "RNA2", slot = "data")[c("CD3D","XIST"),])
```

## Metrics plot

```{r}
methods <- names(datal)
pMetrics <-  plotMetrics(scoresKbet = scoresKbet, scoresSilhouette = scoresSilhouette, methods = methods, nudge_y = 0.01)
```

## Corrections plots original coordinates

```{r}
methods <- names(datal)
plotsOriginal <- lapply(methods, function(m){
  if(m == "Liger"){
    reduction = "Liger"
  }else if(m == "Harmony"){
    reduction = "harmony"
  }else{
    reduction = "pca"
  }
  
  return(plotCorrection(object = datal[[m]], groups = c("batch", "celltype"), reduction = reduction))
})
names(plotsOriginal) <- methods
```

## Corrections plots umap

```{r}
methods <- names(datal)
plotsUmap <- lapply(methods, function(m){
  reduction = "umap"
  
  return(plotCorrection(object = datal[[m]], groups = c("batch", "celltype"), reduction = reduction))
})
names(plotsUmap) <- methods
```

## Features plots

```{r}
methods <- names(datal)
plotsFeatures <- lapply(methods, function(m){
  if(m == "Liger"){
    reduction = "umap"
  }else if(m == "Harmony"){
    reduction = "harmony"
  }else{
    reduction = "pca"
  }
  
  return(plotFeatures(object = datal[[m]], features = c("XIST", "CD3D"), reduction = reduction, colorLimits = c(0, maxExp)))
})
names(plotsFeatures) <- methods
```

## BioRxiv v2 Figure 2.

# Test 3_1_2

```{r fig.height=12, fig.width=16}
plots <- plotsOriginal
pa <- plots[["Uncorrected"]]$batch + ggtitle("Uncorrected", subtitle = "Batch") + mytheme 
pb <- plots[["Uncorrected"]]$celltype + ggtitle("", subtitle = "Celltype") + mytheme
pc <- plotsFeatures[["Uncorrected"]]$XIST + ggtitle("", subtitle = "XIST") + mytheme 
pd <- plotsFeatures[["Uncorrected"]]$CD3D + ggtitle("", subtitle =  "CD3D") + mytheme 
pe <- plots[["Canek"]]$celltype + ggtitle("Canek") + mytheme
pf <- plots[["ComBat"]]$celltype  + ggtitle("ComBat") + mytheme
pg <- plots[["MNN"]]$celltype + ggtitle("MNN") + mytheme
ph <- plots[["Seurat"]]$celltype+ ggtitle("Seurat") + mytheme 
pi <- pMetrics + mytheme

layout <- "
abcd
efii
ghii
"

p <- wrap_plots(a = pa, b = pb , c = pc, d = pd,
                e = pe, f = pf, 
                g = pg, h = ph,
                i = pMetrics,
                design = layout, widths = 1, heights = 1) 

p
```

## Supplementary Figure (celltype & batch)


```{r fig.height=20, fig.width=8}
#plots <- plotsOriginal # Change this to obtain the original coordinates plot
plots <- plotsUmap

pUnco_1 <- plots[["Uncorrected"]]$batch + ggtitle("Uncorrected", subtitle = "Batch") + mytheme
pUnco_2 <- plots[["Uncorrected"]]$celltype + ggtitle("", subtitle = "Celltype") + mytheme

pCanek_1 <- plots[["Canek"]]$batch + ggtitle("Canek", subtitle = "Batch") + mytheme
pCanek_2 <- plots[["Canek"]]$celltype + ggtitle("", subtitle = "Celltype") + mytheme

pMNN_1 <- plots[["MNN"]]$batch + ggtitle("MNN", subtitle = "Batch") + mytheme
pMNN_2 <- plots[["MNN"]]$celltype + ggtitle("", subtitle = "Celltype") + mytheme

pSeurat_1 <- plots[["Seurat"]]$batch + ggtitle("Seurat", subtitle = "Batch") + mytheme
pSeurat_2 <- plots[["Seurat"]]$celltype + ggtitle("", subtitle = "Celltype") + mytheme

pComBat_1 <- plots[["ComBat"]]$batch + ggtitle("ComBat", subtitle = "Batch") + mytheme
pComBat_2 <- plots[["ComBat"]]$celltype + ggtitle("", subtitle = "Celltype") + mytheme

pScanorama_1 <- plots[["Scanorama"]]$batch + ggtitle("Scanorama", subtitle = "Batch") + mytheme
pScanorama_2 <- plots[["Scanorama"]]$celltype + ggtitle("", subtitle = "Celltype") + mytheme

pComBatseq_1 <- plots[["ComBatseq"]]$batch + ggtitle("ComBat-seq", subtitle = "Batch") + mytheme
pComBatseq_2 <- plots[["ComBatseq"]]$celltype + ggtitle("", subtitle = "Celltype") + mytheme

pscMerge_1 <- plots[["scMerge"]]$batch + ggtitle("scMerge", subtitle = "Batch") + mytheme
pscMerge_2 <- plots[["scMerge"]]$celltype + ggtitle("", subtitle = "Celltype") + mytheme

pHarmony_1 <- plots[["Harmony"]]$batch + ggtitle("Harmony", subtitle = "Batch") + mytheme
pHarmony_2 <- plots[["Harmony"]]$celltype + ggtitle("", subtitle = "Celltype") + mytheme

pLiger_1 <- plots[["Liger"]]$batch + ggtitle("Liger", subtitle = "Batch") + mytheme
pLiger_2 <- plots[["Liger"]]$celltype + ggtitle("", subtitle = "Celltype") + mytheme

layout <- "
abcd
efgh
ijkl
mnop
qrst
"

p <- wrap_plots(a = pUnco_1, b = pUnco_2,
                c = pCanek_1, d = pCanek_2,
                e = pComBat_1, f = pComBat_2,
                g = pComBatseq_1, h = pComBatseq_2,
                i = pHarmony_1, j = pHarmony_2,
                k = pLiger_1, l = pLiger_2,
                m = pMNN_1, n = pMNN_2,
                o = pScanorama_1, p = pScanorama_2,
                q = pscMerge_1, r = pscMerge_2,
                s = pSeurat_1, t = pSeurat_2,
                design = layout, widths = 1, heights = 1)

p
```

